On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-03-02 engineering.tex
add intro: sec eng process and sec properties

\subsection{Elicitation of Security Requirements}\label{sec:properties}
Infosec, or Information Security, aims at mitigating the security
risks related to information. The standard de-facto is 
the so called CIA triad (where CIA stands for Confidentiality, Integrity, Availability).

>>>>

Infosec, or Information Security, aims at mitigating the security risks related
to information. The standard de-facto is the so called CIA triad 
(where CIA stands for Confidentiality, Integrity, Availability), which is often
criticized for being too general or non-adequate (e.g. by adding authenticity which is 
often used as a building block for confidentiality and integrity) 
to be effectively applied to the engineering of systems. Due to this,
many researchers an organization tried to improve the CIA triad. 
The evolutions/extensions of the CIA triad has been documented, e.g.,
in \autocite{Samonas2014cia} and is summarized in Table~\ref{tab:ciaevolution}.

\begin{table}[h]
\centering
%\setlength{\tabcolsep}{3.5pt}
%\renewcommand{\arraystretch}{1}
\small
\begin{tabular}{rll} 
	{\bf Year} & {\bf Definition} & {\bf Legend}\\
	\hline
	1970s & infosec = CIA & Confidentiality, Integrity, Availability\\
	1980s & infosec += (Au, nR) & Authenticity and non-Repudiation\\
	1990s & infosec += CSpec & Correctness in Specification\\
	2000s & infosec += RITE & Responsibility, Integrity of people, Trust, Ethicality
\end{tabular}
\caption{Chronological progression of the CIA triad~\label{tab:ciaevolution}}
\end{table}

An example is the effort made by the OECD (Organisation for Economic
Co-operation and Development) in \autocite{OECD2013guidelines} to define
security guidelines for information system (1992) based on new principles such
as ``awareness, ethics, risk assessment'' and maintain those revising the
document (e.g.  following the multistakeholder expert consultation in 2013).
Other similar efforts focused on defining entirely new principles or extending
the CIA triad, such as \autocite{NISTSP800-160}. What is of interest for our
argument is that, to the best of our knowledge, all of the approaches that aim
at improving the CIA triad motivated by empirical evidences. On the contrary,
we now define (in Section~\ref{sec:properties}) the CIA triad for an agent
defined in the $\abftheory$ theory and we test if (i) other properties are
allowed in the $\abftheory$ theory, and (ii) if and how the CIA triad can be
detailed in the $\abftheory$ theory.

\subsection{Elicitation of Security Requirements}\label{sec:properties}
In \autocite{Anderson1972report,Samonas2014cia}, CIA are defined as follows.
\begin{itemize}
	\item Unauthorized information release: an unauthorized person is able
		to read and take  advantage  of  information  stored  in  the
		computer.  This  category of concern  sometimes  extends  to
		``traffic  analysis,''  in  which  the intruder  only observes
		the  patterns  of  information  use.  From  those patterns,
		the  intruder can   infer   some   information   content.
		This category   also   includes   the unauthorized use of a
		proprietary program.  (Confidentiality or Secrecy) 
	\item Unauthorized  information  modification:  an  unauthorized person
		is  able  to make changes in stored information –a form  of
		sabotage.  It should be noted that in the case of this kind of
		violation, the intruder does not necessarily see the
		information he has changed.  (Integrity)
	\item Unauthorized  denial  of  use:  an  intruder  can  prevent  an
		authorized  user  from referring to, or from modifying
		information, even though the intruder may not be able to refer
		to, neither modify the information themselves. (Availability)
\end{itemize}

We now want to generalize the CIA triad to agents and not just 
information and map it to the $\abftheory$ theory.
\begin{definition}{\bf Infosec-Confidentiality --}\label{def:infosec-c}
	An Information $\varphi$ is considered to be confidential over a set of
	agents $Ag_c$ if, per each agent $a\in Ag_c$, the content of the
	information (i.e. the data it carries) can only be understood (i.e. the relation
	between the information and its data can be known) by the
	agents in $Ag_c$.

	\begin{itemize}
		\item[$(\interpretation21)$]
			for all agents $a\in Ag$, $\world\models\information{a}{\varphi}$ and
			$\world\models\rcc(\varphi,Conf) \wedge \neg\dr{Conf}{\varphi}$ iff
			$\world\models\knows{x}{[\information{a'}{\varphi}\rightarrow\varphi]}$
			for any agent $a'$ such that $a'\not\in Ag_c$
	\end{itemize}
\end{definition}

\begin{definition}{\bf System-Confidentiality --}\label{def:confidentiality}
	The property of confidentiality holds in a system when its information
	preserves confidentiality.
\end{definition}

\begin{definition}{\bf Agent-Confidentiality --}\label{def:confidentiality}
An agent preserves the property of confidentiality iff 
\end{definition}
